A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-16 MSR-Scratch.tex
abstract

\begin{abstract}
In this paper, we present a collection of 250K Scratch programs scraped from the Scratch project repository. We processed the program data to encode it into a database that facilitates querying and further analysis. The dataset is intended as an input for research on computing education and source code analysis.
\end{abstract}

>>>>

\begin{abstract}
Scratch is increasingly popular, both as an introductory programming language and as a research target in the computing education research field.	
In this paper, we present an open dataset of 250K recent Scratch programs from 100K authors scraped from the Scratch project repository.
We processed the program data to encode it into a database that facilitates querying and further analysis. We further enriched the dataset with project metadata and with programming mastery scoring results.
The dataset is intended as an input for research on computing education and source code analysis.
Specifically, it can support assessing the programming skills developed in Scratch, exploring the learning progressions of novice programmers, evaluating the quality of Scratch programs, and identifying smells and bad programming practices.
\end{abstract}
